---
output: html_document
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---

```{r setup-198016, eval = F}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
source('scripts/packages.R')
source('scripts/tables.R')

```

```{r  load-data-198016}
my_site <- 198016

```

`r fpr::fpr_appendix_title()`

## Site Location {.unnumbered}

PSCIS crossing `r as.character(my_site)` is located on
`r fpr::fpr_my_pscis_info()`. The site is located on `r fpr_my_pscis_info(col_pull = road_name)`.

<br>

## Background {.unnumbered}

At crossing `r as.character(my_site)`, `r fpr::fpr_my_pscis_info()` is a
`r fpr::fpr_my_bcfishpass() %>% english::ordinal()` order stream with a
watershed area upstream of the crossing of approximately
`r fpr::fpr_my_wshd()`km^2^. The elevation of the watershed ranges from
a maximum of `r fpr::fpr_my_wshd(col = 'elev_max')`m to
`r fpr::fpr_my_wshd(col = 'elev_min')`m near the crossing (Table
\@ref(tab:tab-wshd-198016)). At the time of reporting, there was no fisheries information for areas upstream of crossing
`r as.character(my_site)`.

<br>

```{r tab-wshd-198016, eval = T}
fpr::fpr_table_wshd_sum(site_id = my_site) %>% 
  fpr::fpr_kable(caption_text = paste0('Summary of derived upstream watershed statistics for PSCIS crossing ', my_site, '.'),
           footnote_text = 'Elev P60 = Elevation at which 60% of the watershed area is above',
           scroll = F)

```


<br>

PSCIS stream crossing `r as.character(my_site)` was ranked as a moderate
priority for follow up by the Society for Ecosystem Restoration in Northern BC. A summary of habitat modelling outputs is presented in Table
\@ref(tab:tab-culvert-bcfp-198016). A map of the watershed is provided in
map attachment
[`r fpr::fpr_my_bcfishpass(col_pull = dbm_mof_50k_grid)`](`r fpr::fpr_my_mapsheet()`).

<br>

```{r tab-culvert-bcfp-198016, eval = T}
fpr::fpr_table_bcfp(scroll = gitbook_on) 
```

<br>

## Stream Characteristics at Crossing {.unnumbered}

At the time of the survey, PSCIS crossing `r as.character(my_site)` was
un-embedded, non-backwatered and ranked as a
`r fpr::fpr_my_pscis_info(col_pull = barrier_result) %>% stringr::str_to_lower()` to upstream fish passage according to the provincial protocol
[@moe2011Fieldassessment] (Table \@ref(tab:tab-culvert-198016)). There
was low flow through the culvert at the time of survey. Water temperature was
`r fpr::fpr_my_habitat_info(loc = "ds", col_pull = 'temperature_c')`$^\circ$C,
pH was `r fpr::fpr_my_habitat_info(loc = "ds", col_pull = 'p_h')` and
conductivity was
`r fpr::fpr_my_habitat_info(loc = "ds", col_pull = 'conductivity_m_s_cm')`uS/cm.

`r if(identical(gitbook_on, FALSE)){knitr::asis_output("\\pagebreak")}`
<br>

```{r tab-culvert-198016, eval = T}
fpr::fpr_table_cv_summary_memo()

```

```{r eval=F}
##this is useful to get some comments for the report
hab_site %>% filter(site == my_site & location == 'ds') %>% pull(comments)
hab_site %>% filter(site == my_site & location == 'us') %>% pull(comments)

```

## Stream Characteristics Downstream {.unnumbered}

`r fpr_my_survey_dist(loc = 'ds')`
<!-- `r if(gitbook_on){knitr::asis_output("(Figures \\@ref(fig:photo-198016-01) - \\@ref(fig:photo-198016-02)).")}else(knitr::asis_output("(Figure \\@ref(fig:photo-198016-d01))."))` -->
`r fpr_my_habitat_paragraph(loc = 'ds')` Fish were sighted downstream. There was abundant and functional large woody debris, creating cover and deep pools. The gradient increased near the confluence, with large woody debris jams up to 1m in height forming pools approximately 0.45m deep. There was lots of undercut banks and overhanging vegetation. The stream was partially coupled then fully coupled closer to the confluence. There was one site of bank instability. There appeared to be abundant rearing fish habitat, with suitable overwintering areas and abundant undercut banks. There were gravels throughout, but the gradient was always >5%, which is not ideal for spawning. Overall, the
habitat was rated as `r fpr::fpr_my_priority_info(loc = 'ds')` value for
salmonid rearing and spawning.

## Stream Characteristics Upstream {.unnumbered}

`r fpr_my_survey_dist(loc = 'us')`
<!-- `r if(gitbook_on){knitr::asis_output("(Figures \\@ref(fig:photo-198016-03) - \\@ref(fig:photo-198016-06)).")}else(knitr::asis_output("(Figure \\@ref(fig:photo-198016-d02))."))` -->
`r fpr_my_habitat_paragraph(loc = 'us')` There were sporadic pools and abundant, deep undercut banks. Abundant gravels were present suitable for spawning. Few large and small woody debris steps up to 70cm in height were present. The riparian vegetation consisted primarily of mature spruce trees. The habitat was rated as
`r fpr::fpr_my_priority_info(loc = 'us')` value for salmonid rearing and spawning.

<br>

## Structure Remediation and Cost Estimate {.unnumbered}

Should restoration/maintenance activities proceed, replacement of PSCIS
crossing `r as.character(my_site)` with a bridge
(`r fpr::fpr_my_pscis_info(col_pull = recommended_diameter_or_span_meters)`m
span) is recommended. The cost of the work is estimated at
\$`r format(fpr::fpr_my_cost_estimate(), big.mark = ',')` for a cost
benefit of `r fpr::fpr_my_cost_estimate(col_pull = cost_net)` linear
m/\$1000 and `r fpr::fpr_my_cost_estimate(col_pull = cost_area_net)`
m^2^/\$1000.

<br>

## Conclusion {.unnumbered}

There was
`r fpr::fpr_my_priority_info(col_pull= upstream_habitat_length_km)`km of
habitat modelled upstream of crossing `r as.character(my_site)` with
areas surveyed rated as
`r fpr::fpr_my_priority_info(sit = my_site, loc = 'us', col_pull = hab_value)`
value for salmonid rearing and spawning. `r as.character(my_site)` was ranked as a
`r fpr::fpr_my_priority_info(col_pull = priority)` priority for proceeding to design for replacement. Electrofishing upstream of the culvert is recommended in order to gain insight into the fish population size and density. 

`r if(gitbook_on){knitr::asis_output("<br>")} else knitr::asis_output("\\pagebreak")`

<br>

```{r tab-habitat-summary-198016}
tab_hab_summary %>% 
  filter(Site  == my_site) %>% 
  # select(-Site) %>% 
  fpr::fpr_kable(caption_text = paste0('Summary of habitat details for PSCIS crossing ', my_site, '.'),
                 scroll = F) 

```
