
```{r setup-test, include=T}
my_site <- 124420
my_site2 <- 124422
```

# test
Should restoration/maintenance activities proceed at the site, replacement of PSCIS crossing `r as.character(my_site)` with a bridge (`r fpr::fpr_my_pscis_info(col_pull = recommended_diameter_or_span_meters)`m span) is recommended. The cost of the work is estimated at \$`r format(fpr::fpr_my_cost_estimate(), big.mark = ',')` for a cost benefit of `r fpr::fpr_my_cost_estimate(col_pull = cost_net)` linear m/\$1000 and `r fpr::fpr_my_cost_estimate(col_pull = cost_area_net)` m^2^/\$1000.


```{r test-off, eval=F}
# The stream was surveyed downstream from the culvert for `r fpr::fpr_my_priority_info(loc = 'ds', col_pull = 'length_surveyed')`m `r if(gitbook_on){knitr::asis_output("(Figures \\@ref(fig:photo-198048-01) - \\@ref(fig:photo-198048-02))")}else(knitr::asis_output("(Figure \\@ref(fig:photo-198048-d01))"))`. Total cover amount was rated as `r fpr::fpr_my_habitat_cover(loc = 'ds', cover_type = 'total cover')` with  `r fpr::fpr_my_habitat_cover(loc = 'ds', cover_type = 'dominant')` dominant. Cover was also present as `r fpr::fpr_my_habitat_cover(loc = 'ds', cover_type = 'sub-dominant')` (Table \@ref(tab:tab-habitat-summary-198048)). The average channel width was `r fpr::fpr_my_habitat_info(loc = 'ds', col_pull = 'avg_channel_width_m')`m, the average wetted width was `r fpr::fpr_my_habitat_info(loc = 'ds', col_pull = 'avg_wetted_width_m')`m and the average gradient was `r fpr::fpr_my_habitat_info(loc = 'ds', col_pull = 'average_gradient_percent')`%. The dominant substrate was `r fpr::fpr_my_habitat_info(loc = 'ds', col_pull = "bed_material_dominant")` with `r fpr::fpr_my_habitat_info(loc = 'ds', col_pull = "bed_material_subdominant")` subdominant.  The habitat was rated as `r fpr::fpr_my_priority_info(loc = 'ds')` value for salmonid rearing and spawning. 

fpr_my_survey_dist <- function(loc = 'us'){
    
    seg1 <- 'The stream was surveyed '
    
    if(identical(loc, 'us')){
    seg2 <- 'upstream '}else 'downstream'
    
    seg3 <- 'from the culvert for '
    
    seg4 <- fpr::fpr_my_priority_info(loc = loc, col_pull = 'length_surveyed')
    
    seg5 <- 'm '
    
    paste0(seg1, seg2, seg3, seg4, seg5)
}

fpr_my_survey_dist(loc = 'ds')


fpr_my_cover_sentence <- function(loc = 'us'){
  seg1 <- 'Total cover amount was rated as '
  
  seg2 <- fpr::fpr_my_habitat_cover(loc = loc, cover_type = 'total cover')
  
  seg3 <- 'with '
  
  seg4 <- fpr::fpr_my_habitat_cover(loc = loc, cover_type = 'dominant')
  
  seg5 <- ' dominant. Cover was also present as '
  
  seg6 <- fpr::fpr_my_habitat_cover(loc = loc, cover_type = 'sub-dominant')
  
  paste0(seg1, seg2, seg3, seg4, seg5, seg6)
}

fpr_my_survey_dist(loc = 'ds') 
fpr_my_cover_sentence()


```

Does this.
Put commas.
Between.
